Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-25 paper/paper.tex
Iterate section 4

Spanner provides different operations, as shown in Table~\ref{tbl:reads-writes}.
Read-only transactions have to be made explicit. This requires the
application/user to predeclare that the read-only transaction does not include
write operations. Moreover, read-only transaction have the benefits of snapshot
isolation because they are \emph{lock-free}. Standalone writes are simply
read-write transaction without any read operations. Non-snapshot standalone reads
are implemented as read-only transactions. In contrast to snapshot reads, which
may be executed on any timestamp in the past, read-only transactions execute on
the last committed timestamp. Both, snapshot reads and read-only transactions,
proceed on any \emph{sufficiently up-to-date} replica. For snapshot reads,
the application/user has two options. On the one hand, a precise timestamp can
be specified at which the read should be executed. On the other hand, an upper
bound can be specified, and Spanner choses a timestamp that satisfies this bound.

@@

Read-write transactions use two-phase locking, and Spanner may only assign
timestamps in between the two phases. Spanner enforces another invariant, the
a \emph{monotonicity invariant}, which makes use of the disjointness invariant.
This monotonicity invariant guarantees that within each Paxos group, Spanner
assigns timestamps to Paxos writes in monotonically increasing order. To guarantee
this across leaders, Spanner utilizes the disjointness invariant. This implies
that a leader must only assign timestamps within the interval of its leader
lease. $s_{max}$ is advanced to $s$ whenever a timestamp $s$ is assigned by a
leader.

>>>>

Spanner provides different operations, as shown in Table~\ref{tbl:reads-writes}.
Read-only transactions have to be made explicit. This requires the
application/user to predeclare that the read-only transaction does not include
write operations. Moreover, read-only transaction have the benefits of snapshot
isolation because they are \emph{lock-free}. Standalone writes are simply
read-write transaction without any read operations. Non-snapshot standalone reads
are implemented as read-only transactions. In contrast to snapshot reads, which
may be executed on any timestamp in the past, read-only transactions execute on
the last committed write timestamp. Both, snapshot reads and read-only
transactions, proceed on any \emph{sufficiently up-to-date} replica. For snapshot
reads, the application/user has two options. On the one hand, a precise timestamp
can be specified at which the read should be executed. On the other hand, an upper
bound can be specified, and Spanner choses a timestamp that satisfies this bound.

@@

Read-write transactions use two-phase locking, and Spanner may only assign
timestamps in between the two phases. Spanner enforces another invariant, the
\emph{monotonicity invariant}, which makes use of the disjointness invariant.
This monotonicity invariant guarantees that within each Paxos group, Spanner
assigns timestamps to Paxos writes in monotonically increasing order. To guarantee
this across leaders, Spanner utilizes the disjointness invariant. This implies
that a leader must only assign timestamps within the interval of its leader
lease. $s_{max}$ is advanced to $s$ whenever a timestamp $s$ is assigned by a
leader.
